Default GMSE data structures

### 2020-05-21 notebook/ms/SI7.Rmd
Update the vignette here to account for the new columns in the agents array, just a heads up @jejoenje if you're editing the land parts

1. ID (each agent gets a unique number)
2. Type 1 (0 indicates the manager; 1 indicates users)
3. Type 2 (currently unused)
4. Type 3 (currently unused)
5. x-location on the landscape (typically ignored)
6. y-location on the landscape (typically ignored)
7. Movement distance (typically ignored)
8. Time parameter (typically ignored)
9. Distance of vision (currently used only for managers)
10. Error parameter (currently unused)
11. Resource marking parameter (currently used only for managers)
12. Resource tally parameter (currently used only for managers)
13. How many resources an agent has in view (unused)
14. Total number of cells owned by an agent
15. Unused column
16. Yield from owned land (zero for users when default `land_ownership = FALSE`)
17. Budget

It is obvious from the above list that most columns represent traits that are either typically ignored or currently not in use. This is intended to allow for easier future development of default model options and potential customisation of sub-models in `gmse_apply`. We anticipate that future versions of GMSE will contain multiple user types with unique traits and among-user interactions.

@@

```{r, echo = FALSE, fig.height = 5, fig.width = 5}
par(mar = c(0.2, 0.2, 0.2, 0.2));
land_1 <- owner_land_ssa(dim_x = 64, dim_y = 64, owners = 8, public_land = 0);
image(land_1, xaxt = "n", yaxt = "n", col = topo.colors(max(land_1)));
```

@@

```{r, echo = FALSE, fig.height = 4, fig.width = 5}
par(mar = c(0.2, 0.2, 0.2, 0.2));
land_2 <- owner_land_ssa(dim_x = 100, dim_y = 80, owners = 9, public_land = 0);
image(land_2, xaxt = "n", yaxt = "n", col = topo.colors(max(land_2)));
```

@@

```{r, echo = FALSE, fig.height = 5, fig.width = 5}
par(mar = c(0.2, 0.2, 0.2, 0.2));
land_3 <- owner_land_ssa(dim_x = 100, dim_y = 100, owners = 7, 
                         public_land = 0.5);
image(land_3, xaxt = "n", yaxt = "n", col = topo.colors(max(land_3)));
```

@@

```{r, echo = FALSE, fig.height = 5, fig.width = 5}
par(mar = c(0.2, 0.2, 0.2, 0.2));
land_4 <- owner_land_ssa(dim_x = 100, dim_y = 100, owners = 7, 
                         public_land = 0.1);
image(land_4, xaxt = "n", yaxt = "n", col = topo.colors(max(land_4)));
```

>>>>

1. ID (each agent gets a unique number)
2. Type 1 (0 indicates the manager; 1 indicates users)
3. Type 2 (currently unused)
4. Type 3 (currently unused)
5. x-location on the landscape (typically ignored)
6. y-location on the landscape (typically ignored)
7. Movement distance (typically ignored)
8. Time parameter (typically ignored)
9. Distance of vision (currently used only for managers)
10. Error parameter (currently unused)
11. Resource marking parameter (currently used only for managers)
12. Resource tally parameter (currently used only for managers)
13. How many resources an agent has in view (unused)
14. Total number of cells owned by an agent
15. Unused column
16. Yield from owned land (zero for users when default `land_ownership = FALSE`)
17. Agent's baseline budget
18. Agent's perception of the efficacy of scaring one resource
19. Agent's perception of the efficacy of culling one resource
20. Agent's perception of the efficacy of castrating one resource
21. Agent's perception of the efficacy of feeding one resource
22. Agent's perception of the efficacy of helping offspring of one resource
23. Agent's perception of the efficacy of tending the crop on one landscape cell
24. Agent's perception of the efficacy of killing the crop on one landscape cell
25. Increment added to the manager's (row 1) baseline budget caused by a budget bonus
26. Increment added to an agent's budget caused by yield
27. Unused column

Note that for the perceptions of the efficacy of different actions (columns 18-24), this relates to whatever it is that the agents are acting upon. For example, for columns 18-22, actions are on the resources, so if an agent's perception of the efficacy of scaring is -1, this means that they believe that scaring a resource will decrease the number of resources affecting them by 1 (lower default values for landowners are caused based on the probability of a scared resource landing on a different cell owned by the same agent). For columns 23-24, actions are on the landscape, so if an agent tends the crop on one landscape cell, this value defines an agent's perception of how much yield on that cell will increase.

It is obvious from the above list that several columns represent traits that are either typically ignored or currently not in use. This is intended to allow for easier future development of default model options and potential customisation of sub-models in `gmse_apply`. We anticipate that future versions of GMSE will contain multiple user types with unique traits and among-user interactions.

@@

```{r, echo = FALSE, fig.height = 5, fig.width = 5}
par(mar = c(0.2, 0.2, 0.2, 0.2));
land_1 <- owner_land_ssa(dim_x = 64, dim_y = 64, owners = 8, public_land = 0, 
                         land_var = 0);
image(land_1, xaxt = "n", yaxt = "n", col = topo.colors(max(land_1)));
```

@@

```{r, echo = FALSE, fig.height = 4, fig.width = 5}
par(mar = c(0.2, 0.2, 0.2, 0.2));
land_2 <- owner_land_ssa(dim_x = 100, dim_y = 80, owners = 9, public_land = 0,
                         land_var = 0);
image(land_2, xaxt = "n", yaxt = "n", col = topo.colors(max(land_2)));
```

@@

```{r, echo = FALSE, fig.height = 5, fig.width = 5}
par(mar = c(0.2, 0.2, 0.2, 0.2));
land_3 <- owner_land_ssa(dim_x = 100, dim_y = 100, owners = 7, 
                         public_land = 0.5, land_var = 0);
image(land_3, xaxt = "n", yaxt = "n", col = topo.colors(max(land_3)));
```

@@

```{r, echo = FALSE, fig.height = 5, fig.width = 5}
par(mar = c(0.2, 0.2, 0.2, 0.2));
land_4 <- owner_land_ssa(dim_x = 100, dim_y = 100, owners = 7, 
                         public_land = 0.1, land_var = 0);
image(land_4, xaxt = "n", yaxt = "n", col = topo.colors(max(land_4)));
```
